Two Decades of Smalltalk VM Development

### 2018-08-16 paper.tex
improved opening with GT in conclusion

\begin{figure*}[ht!]
		\centering
		\includegraphics[width=0.9\linewidth]{figures/SimulatedMemory}
		\caption{Runtime Memory and Simulated Counter-Part}
		\label{fig:SimulatedMemory}
\end{figure*}

@@

We introduced and discussed the \openSmalltalkVM simulation infrastructure, used to develop and debug the VM. We believe it is a powerful tool allowing to reduce our development time and to allow to fix bugs quickly. In the near future, we plan to extend the simulator with customizable development tools, especially the moldable inspectors and debuggers \cite{MoldableInspector, MoldableDebugger}, to have a fancy user interface on top of the current simulation model, currently quite tricky to apprehend by new developers.

>>>>

\begin{figure*}[ht!]
		\centering
		\includegraphics[width=0.95\linewidth]{figures/SimulatedMemory}
		\caption{Runtime Memory and Simulated Counter-Part}
		\label{fig:SimulatedMemory}
\end{figure*}

@@

We introduced and discussed the \openSmalltalkVM simulation infrastructure, used to develop and debug the VM. We believe it is a powerful tool allowing to reduce our development time and to allow to fix bugs quickly.

In the near future, we plan to extend the simulator with customizable development tools. Currently the tools built in top of the simulation infrastructure is mainly textual. Frameworks such as the moldable inspectors and debuggers \cite{MoldableInspector, MoldableDebugger} will allow us to have a more interactive interface, making it easier to apprehend by new developers.
